Manuscript progress report

### 2024-05-28 Docs/manuscript.tex
presentation papers

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}

@@

\title{Manuscript progress report}
\author{Ying Jin}
\date{2024-02-16}

@@

{
\setcounter{tocdepth}{3}
\tableofcontents
}
\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{assumptions}{%
\subsection{Assumptions}\label{assumptions}}

@@

\hypertarget{observed-data}{%
\subsection{Observed data}\label{observed-data}}

@@

\hypertarget{fgfpca-algorithm}{%
\subsection{fGFPCA Algorithm}\label{fgfpca-algorithm}}

\hypertarget{bin-data}{%
\subsubsection{Bin data:}\label{bin-data}}

@@

\hypertarget{local-glmms}{%
\subsubsection{Local GLMMs}\label{local-glmms}}

@@

\hypertarget{fpca}{%
\subsubsection{FPCA}\label{fpca}}

@@

\hypertarget{projection-and-debias}{%
\subsubsection{Projection and Debias}\label{projection-and-debias}}

@@

\hypertarget{out-of-sample-prediction}{%
\subsection{Out-of-sample prediction}\label{out-of-sample-prediction}}

@@

\hypertarget{reference-method}{%
\section{Reference method}\label{reference-method}}

\hypertarget{glmmadaptive}{%
\subsection{GLMMadaptive}\label{glmmadaptive}}

@@

\hypertarget{generalized-functional-on-scalar-regression}{%
\subsection{Generalized functional-on-scalar
regression}\label{generalized-functional-on-scalar-regression}}

@@

\hypertarget{larger-scale-simulation}{%
\section{Larger-scale simulation}\label{larger-scale-simulation}}

\hypertarget{simulation-set-up}{%
\subsection{Simulation set up}\label{simulation-set-up}}

@@

\hypertarget{figures}{%
\subsection{Figures}\label{figures}}

@@

\includegraphics{manuscript_files/figure-latex/fig_large_sim-1.pdf}

\hypertarget{ise-and-auc}{%
\subsection{ISE and AUC}\label{ise-and-auc}}

@@

\begin{landscape}\begin{table}
\centering
\begin{tabular}{lrrrrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{16}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-17}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{fGFPCA} & \multicolumn{4}{c}{GFOSR (L=5)} & \multicolumn{4}{c}{GFOSR (L=1)} & \multicolumn{4}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13} \cmidrule(l{3pt}r{3pt}){14-17}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\midrule
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{ISE}}\\
\hspace{1em}(0.2, 0.4] & 146.407 &  &  &  & 274.947 &  &  &  & 362.476 &  &  &  & 387.708 &  &  & \\
\hspace{1em}(0.4, 0.6] & 183.967 & 74.977 &  &  & 277.438 & 220.209 &  &  & 286.614 & 262.552 &  &  & 291.579 & 269.799 &  & \\
\hspace{1em}(0.6, 0.8] & 218.265 & 49.275 & 15.776 &  & 322.338 & 373.108 & 325.017 &  & 385.701 & 410.508 & 389.305 &  & 315.778 & 282.736 & 278.242 & \\
\hspace{1em}(0.8, 1.0] & 108.918 & 77.981 & 17.747 & 12.005 & 290.982 & 318.079 & 350.850 & 333.580 & 328.482 & 341.274 & 354.211 & 347.067 & 563.011 & 477.485 & 597.746 & 600.340\\
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{AUC}}\\
\hspace{1em}(0.2, 0.4] & 0.748 &  &  &  & 0.686 &  &  &  & 0.624 &  &  &  & 0.591 &  &  & \\
\hspace{1em}(0.4, 0.6] & 0.664 & 0.734 &  &  & 0.563 & 0.630 &  &  & 0.543 & 0.590 &  &  & 0.524 & 0.596 &  & \\
\hspace{1em}(0.6, 0.8] & 0.715 & 0.790 & 0.803 &  & 0.669 & 0.628 & 0.676 &  & 0.604 & 0.577 & 0.615 &  & 0.669 & 0.694 & 0.687 & \\
\hspace{1em}(0.8, 1.0] & 0.740 & 0.755 & 0.781 & 0.784 & 0.626 & 0.606 & 0.552 & 0.584 & 0.588 & 0.564 & 0.537 & 0.551 & 0.514 & 0.556 & 0.526 & 0.564\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

\hypertarget{time-minutes}{%
\subsection{Time (minutes)}\label{time-minutes}}

I chose not to report fitting and prediction time separately because it
is too difficult to tell them apart for the GFOSR models.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{data.frame}\NormalTok{(}
  \StringTok{"Method"} \OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{"fGFPCA"}\NormalTok{, }\StringTok{"GLMMadaptive"}\NormalTok{, }\StringTok{"GFOSR (L=1)"}\NormalTok{, }\StringTok{"GFOSR (L=5)"}\NormalTok{),}
  \StringTok{"Time"} \OtherTok{=} \FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(fit\_time}\SpecialCharTok{/}\DecValTok{60}\SpecialCharTok{+}\NormalTok{pred\_time),}
             \FunctionTok{mean}\NormalTok{(fit\_time\_ref}\SpecialCharTok{+}\NormalTok{pred\_time\_ref}\SpecialCharTok{/}\DecValTok{60}\NormalTok{),}
             \FunctionTok{mean}\NormalTok{(t\_vec\_gfosr\_l1}\SpecialCharTok{/}\DecValTok{60}\NormalTok{), }
             \FunctionTok{mean}\NormalTok{(t\_vec\_gfosr\_l5}\SpecialCharTok{/}\DecValTok{60}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable}\NormalTok{(}\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{booktabs =}\NormalTok{ T, }\AttributeTok{table.attr =} \StringTok{"style = }\SpecialCharTok{\textbackslash{}"}\StringTok{color:black;}\SpecialCharTok{\textbackslash{}"}\StringTok{"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{full\_width =}\NormalTok{ F) }
\end{Highlighting}
\end{Shaded}

\begin{table}
\centering
\begin{tabular}{lr}
\toprule
Method & Time\\
\midrule
fGFPCA & 2.317\\
GLMMadaptive & 2.304\\
GFOSR (L=1) & 0.025\\
GFOSR (L=5) & 0.144\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{small-scale-simulation}{%
\section{Small-scale simulation}\label{small-scale-simulation}}

@@

\hypertarget{figure}{%
\subsection{Figure}\label{figure}}

@@

\includegraphics{manuscript_files/figure-latex/fig_small_sim-1.pdf}

\hypertarget{ise-and-auc-1}{%
\subsection{ISE and AUC}\label{ise-and-auc-1}}

@@

\begin{landscape}\begin{table}
\centering
\begin{tabular}{lrrrrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{16}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-17}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{fGFPCA} & \multicolumn{4}{c}{GFOSR (L=5)} & \multicolumn{4}{c}{GFOSR (L=1)} & \multicolumn{4}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13} \cmidrule(l{3pt}r{3pt}){14-17}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\midrule
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{ISE}}\\
\hspace{1em}(0.2, 0.4] & 150.641 &  &  &  & 286.853 &  &  &  & 367.282 &  &  &  & 374.836 &  &  & \\
\hspace{1em}(0.4, 0.6] & 188.065 & 77.380 &  &  & 286.628 & 227.225 &  &  & 290.781 & 265.809 &  &  & 268.390 & 463.337 &  & \\
\hspace{1em}(0.6, 0.8] & 224.001 & 51.533 & 16.879 &  & 328.612 & 374.572 & 326.522 &  & 386.705 & 408.427 & 388.427 &  & 319.731 & 287.001 & 233.510 & \\
\hspace{1em}(0.8, 1.0] & 112.163 & 81.368 & 19.592 & 13.399 & 301.165 & 324.817 & 353.888 & 335.139 & 331.488 & 342.935 & 354.800 & 347.627 & 228.335 & 469.769 & 331.509 & 131.993\\
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{AUC}}\\
\hspace{1em}(0.2, 0.4] & 0.746 &  &  &  & 0.679 &  &  &  & 0.620 &  &  &  & 0.672 &  &  & \\
\hspace{1em}(0.4, 0.6] & 0.662 & 0.734 &  &  & 0.549 & 0.627 &  &  & 0.536 & 0.590 &  &  & 0.622 & 0.671 &  & \\
\hspace{1em}(0.6, 0.8] & 0.710 & 0.787 & 0.801 &  & 0.656 & 0.617 & 0.668 &  & 0.598 & 0.574 & 0.613 &  & 0.689 & 0.698 & 0.731 & \\
\hspace{1em}(0.8, 1.0] & 0.740 & 0.754 & 0.781 & 0.784 & 0.611 & 0.588 & 0.551 & 0.578 & 0.580 & 0.556 & 0.536 & 0.551 & 0.681 & 0.629 & 0.679 & 0.743\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

@@

\hypertarget{time}{%
\section{Time}\label{time}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{data.frame}\NormalTok{(}
  \StringTok{"Method"} \OtherTok{=} \FunctionTok{c}\NormalTok{(}\StringTok{"fGFPCA"}\NormalTok{, }\StringTok{"GLMMadaptive"}\NormalTok{, }\StringTok{"GFOSR (L=1)"}\NormalTok{, }\StringTok{"GFOSR (L=5)"}\NormalTok{),}
  \StringTok{"Time"} \OtherTok{=} \FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(fit\_time\_subset\_fGFPCA}\SpecialCharTok{/}\DecValTok{60}\SpecialCharTok{+}\NormalTok{pred\_time\_subset\_fGFPCA),}
             \FunctionTok{mean}\NormalTok{(fit\_time\_subset\_adglmm}\SpecialCharTok{+}\NormalTok{pred\_time\_subset\_adglmm}\SpecialCharTok{/}\DecValTok{60}\NormalTok{),}
             \FunctionTok{mean}\NormalTok{(t\_subset\_gfosr\_l1}\SpecialCharTok{/}\DecValTok{60}\NormalTok{), }
             \FunctionTok{mean}\NormalTok{(t\_subset\_gfosr\_l5}\SpecialCharTok{/}\DecValTok{60}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable}\NormalTok{(}\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{booktabs =}\NormalTok{ T, }\AttributeTok{table.attr =} \StringTok{"style = }\SpecialCharTok{\textbackslash{}"}\StringTok{color:black;}\SpecialCharTok{\textbackslash{}"}\StringTok{"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{full\_width =}\NormalTok{ F) }
\end{Highlighting}
\end{Shaded}

\begin{table}
\centering
\begin{tabular}{lr}
\toprule
Method & Time\\
\midrule
fGFPCA & 1.629\\
GLMMadaptive & 5.479\\
GFOSR (L=1) & 0.010\\
GFOSR (L=5) & 0.054\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{nhanes-data-application}{%
\section{NHANES data application}\label{nhanes-data-application}}

@@

\hypertarget{auc}{%
\subsection{AUC}\label{auc}}

@@

\begin{landscape}\begin{table}
\centering
\begin{tabular}{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{12}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-13}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{fGFPCA} & \multicolumn{3}{c}{GFOSR (L=5)} & \multicolumn{3}{c}{GFOSR (L=1)} & \multicolumn{3}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
Window & 6am & 12pm & 6pm & 6am & 12pm & 6pm & 6am & 12pm & 6pm & 6am & 12pm & 6pm\\
\midrule
6am-12pm & 0.703 &  &  & 0.689 &  &  & 0.684 &  &  & 0.581 &  & \\
12pm-6pm & 0.536 & 0.709 &  & 0.519 & 0.699 &  & 0.520 & 0.654 &  & 0.532 & 0.701 & \\
6pm-12am & 0.716 & 0.679 & 0.773 & 0.677 & 0.678 & 0.723 & 0.677 & 0.676 & 0.708 & 0.514 & 0.565 & 0.626\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

\hypertarget{figure-1}{%
\subsection{Figure}\label{figure-1}}

@@

\includegraphics{manuscript_files/figure-latex/fig_appl-1.pdf}

@@

\hypertarget{additional-figures}{%
\section{Additional figures}\label{additional-figures}}

>>>>

\usepackage{bookmark}

@@

\title{Manuscript progress report}
\author{Ying Jin}
\date{2024-05-28}

@@

{
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{Method}\label{method}

\subsection{Assumptions}\label{assumptions}

@@

\subsection{Observed data}\label{observed-data}

@@

\subsection{fGFPCA Algorithm}\label{fgfpca-algorithm}

\subsubsection{Bin data:}\label{bin-data}

@@

\subsubsection{Local GLMMs}\label{local-glmms}

@@

\subsubsection{FPCA}\label{fpca}

@@

\subsubsection{Projection and Debias}\label{projection-and-debias}

@@

\subsection{Out-of-sample prediction}\label{out-of-sample-prediction}

@@

\section{Reference method}\label{reference-method}

\subsection{GLMMadaptive}\label{glmmadaptive}

@@

\subsection{Generalized functional-on-scalar
regression}\label{generalized-functional-on-scalar-regression}

@@

\section{Larger-scale simulation}\label{larger-scale-simulation}

\subsection{Simulation set up}\label{simulation-set-up}

@@

\subsection{Figures}\label{figures}

@@

\includegraphics{manuscript_files/figure-latex/fig_large_sim_paper-1.pdf}
\NormalTok{  pred\_list\_all[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{580}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
\NormalTok{  pred\_list\_ref[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{580}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{  pred\_list\_gfosr\_l1[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{580}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{  pred\_list\_gfosr\_l5[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{580}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{facet\_grid}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{vars}\NormalTok{(method))}\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{col =} \StringTok{"Maximum observation time"}\NormalTok{, }\AttributeTok{x =} \StringTok{"t"}\NormalTok{, }\AttributeTok{y=}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ cols, }\AttributeTok{guide=}\StringTok{"none"}\NormalTok{)}

\includegraphics{manuscript_files/figure-latex/fig_large_sim_pre-1.pdf}

\subsection{ISE and AUC}\label{ise-and-auc}

@@

\begin{landscape}
\begin{longtable}[t]{lrrrrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{16}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-17}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{fGFPCA} & \multicolumn{4}{c}{GFOSR (L=5)} & \multicolumn{4}{c}{GFOSR (L=1)} & \multicolumn{4}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13} \cmidrule(l{3pt}r{3pt}){14-17}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\midrule
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{ISE}}\\
\hspace{1em}(0.2, 0.4] & 146.405 &  &  &  & 274.947 &  &  &  & 362.476 &  &  &  & 387.708 &  &  & \\
\hspace{1em}(0.4, 0.6] & 183.965 & 74.979 &  &  & 277.438 & 220.209 &  &  & 286.614 & 262.552 &  &  & 291.579 & 269.799 &  & \\
\hspace{1em}(0.6, 0.8] & 218.264 & 49.287 & 15.788 &  & 322.338 & 373.108 & 325.017 &  & 385.701 & 410.508 & 389.305 &  & 315.778 & 282.736 & 278.242 & \\
\hspace{1em}(0.8, 1.0] & 108.914 & 77.985 & 17.759 & 12.018 & 290.982 & 318.079 & 350.850 & 333.580 & 328.482 & 341.274 & 354.211 & 347.067 & 563.011 & 477.485 & 597.746 & 600.340\\
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{AUC}}\\
\hspace{1em}(0.2, 0.4] & 0.748 &  &  &  & 0.686 &  &  &  & 0.624 &  &  &  & 0.591 &  &  & \\
\hspace{1em}(0.4, 0.6] & 0.664 & 0.734 &  &  & 0.563 & 0.630 &  &  & 0.543 & 0.590 &  &  & 0.524 & 0.596 &  & \\
\hspace{1em}(0.6, 0.8] & 0.715 & 0.790 & 0.803 &  & 0.669 & 0.628 & 0.676 &  & 0.604 & 0.577 & 0.615 &  & 0.669 & 0.694 & 0.687 & \\
\hspace{1em}(0.8, 1.0] & 0.740 & 0.755 & 0.781 & 0.784 & 0.626 & 0.606 & 0.552 & 0.584 & 0.588 & 0.564 & 0.537 & 0.551 & 0.514 & 0.556 & 0.526 & 0.564\\
\bottomrule
\end{longtable}
\end{landscape}

\section{Small-scale simulation}\label{small-scale-simulation}

@@

\subsection{Figure}\label{figure}

@@

\includegraphics{manuscript_files/figure-latex/fig_small_sim_paper-1.pdf}
\NormalTok{sep\_plot }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
\NormalTok{  pred\_subset\_fGFPCA[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{189}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method=}\StringTok{"fGFPCA"}\NormalTok{),}
\NormalTok{  pred\_subset\_gfosr\_l5[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{189}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=5)"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
\NormalTok{  pred\_subset\_gfosr\_l1[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{189}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=1)"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
\NormalTok{  pred\_subset\_adglmm[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id}\SpecialCharTok{==}\DecValTok{189}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GLMMadaptive"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{facet\_grid}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{vars}\NormalTok{(method))}\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{col =} \StringTok{"Maximum observation time"}\NormalTok{, }\AttributeTok{x =} \StringTok{"t"}\NormalTok{, }\AttributeTok{y=}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{by =} \FloatTok{0.2}\NormalTok{))}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sep\_plot}\SpecialCharTok{+}\FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ cols, }\AttributeTok{guide=}\StringTok{"none"}\NormalTok{)}\SpecialCharTok{+}
  \CommentTok{\#theme(legend.position = "bottom")+}
  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ cols, }\AttributeTok{guide =} \StringTok{"none"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Scale for colour is already present.
## Adding another scale for colour, which will replace the existing scale.
\end{verbatim}

\includegraphics{manuscript_files/figure-latex/fig_small_sim_pre-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{as\_ggplot}\NormalTok{(ggpubr}\SpecialCharTok{::}\FunctionTok{get\_legend}\NormalTok{(sep\_plot}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}\SpecialCharTok{+}
                               \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ cols)))}
\end{Highlighting}
\end{Shaded}

\includegraphics{manuscript_files/figure-latex/legend-1.pdf}

\subsection{ISE and AUC}\label{ise-and-auc-1}

@@

\begin{landscape}
\begin{longtable}[t]{lrrrrrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{16}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-17}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{fGFPCA} & \multicolumn{4}{c}{GFOSR (L=5)} & \multicolumn{4}{c}{GFOSR (L=1)} & \multicolumn{4}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13} \cmidrule(l{3pt}r{3pt}){14-17}
Window & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8 & 0.2 & 0.4 & 0.6 & 0.8\\
\midrule
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{ISE}}\\
\hspace{1em}(0.2, 0.4] & 150.636 &  &  &  & 286.853 &  &  &  & 367.282 &  &  &  & 374.836 &  &  & \\
\hspace{1em}(0.4, 0.6] & 188.095 & 77.401 &  &  & 286.628 & 227.225 &  &  & 290.781 & 265.809 &  &  & 268.390 & 463.337 &  & \\
\hspace{1em}(0.6, 0.8] & 224.067 & 51.634 & 16.969 &  & 328.612 & 374.572 & 326.522 &  & 386.705 & 408.427 & 388.427 &  & 319.731 & 287.001 & 233.510 & \\
\hspace{1em}(0.8, 1.0] & 112.190 & 81.407 & 19.701 & 13.485 & 301.165 & 324.817 & 353.888 & 335.139 & 331.488 & 342.935 & 354.800 & 347.627 & 228.335 & 469.769 & 331.509 & 131.993\\
\addlinespace[0.3em]
\multicolumn{17}{l}{\textbf{AUC}}\\
\hspace{1em}(0.2, 0.4] & 0.746 &  &  &  & 0.679 &  &  &  & 0.620 &  &  &  & 0.672 &  &  & \\
\hspace{1em}(0.4, 0.6] & 0.662 & 0.734 &  &  & 0.549 & 0.627 &  &  & 0.536 & 0.590 &  &  & 0.622 & 0.671 &  & \\
\hspace{1em}(0.6, 0.8] & 0.710 & 0.787 & 0.801 &  & 0.656 & 0.617 & 0.668 &  & 0.598 & 0.574 & 0.613 &  & 0.689 & 0.698 & 0.731 & \\
\hspace{1em}(0.8, 1.0] & 0.740 & 0.754 & 0.781 & 0.784 & 0.611 & 0.588 & 0.551 & 0.578 & 0.580 & 0.556 & 0.536 & 0.551 & 0.681 & 0.629 & 0.679 & 0.743\\
\bottomrule
\end{longtable}
\end{landscape}

@@

\section{Time}\label{time}

Average time per iteration in minutes

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{time\_tb }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{sim1 =} \FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(fit\_time}\SpecialCharTok{/}\DecValTok{60}\SpecialCharTok{+}\NormalTok{pred\_time),}
             \FunctionTok{mean}\NormalTok{(fit\_time\_ref}\SpecialCharTok{+}\NormalTok{pred\_time\_ref}\SpecialCharTok{/}\DecValTok{60}\NormalTok{),}
             \FunctionTok{mean}\NormalTok{(t\_vec\_gfosr\_l1}\SpecialCharTok{/}\DecValTok{60}\NormalTok{), }
             \FunctionTok{mean}\NormalTok{(t\_vec\_gfosr\_l5}\SpecialCharTok{/}\DecValTok{60}\NormalTok{)),}
           \AttributeTok{sim2 =} \FunctionTok{c}\NormalTok{(}\FunctionTok{mean}\NormalTok{(fit\_time\_subset\_fGFPCA}\SpecialCharTok{/}\DecValTok{60}\SpecialCharTok{+}\NormalTok{pred\_time\_subset\_fGFPCA),}
             \FunctionTok{mean}\NormalTok{(fit\_time\_subset\_adglmm}\SpecialCharTok{+}\NormalTok{pred\_time\_subset\_adglmm}\SpecialCharTok{/}\DecValTok{60}\NormalTok{),}
             \FunctionTok{mean}\NormalTok{(t\_subset\_gfosr\_l1}\SpecialCharTok{/}\DecValTok{60}\NormalTok{), }
             \FunctionTok{mean}\NormalTok{(t\_subset\_gfosr\_l5}\SpecialCharTok{/}\DecValTok{60}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{t}\NormalTok{()}
\FunctionTok{colnames}\NormalTok{(time\_tb) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"fGFPCA"}\NormalTok{, }\StringTok{"GLMMadaptive"}\NormalTok{, }\StringTok{"GFOSR (L=1)"}\NormalTok{, }\StringTok{"GFOSR (L=5)"}\NormalTok{)}
\FunctionTok{rownames}\NormalTok{(time\_tb) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Simulation 1"}\NormalTok{, }\StringTok{"Simulation 2"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{time\_tb }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{kable}\NormalTok{(}\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{booktabs =}\NormalTok{ T, }\AttributeTok{table.attr =} \StringTok{"style = }\SpecialCharTok{\textbackslash{}"}\StringTok{color:black;}\SpecialCharTok{\textbackslash{}"}\StringTok{"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{full\_width =}\NormalTok{ F) }
\end{Highlighting}
\end{Shaded}

\begin{longtable}[t]{lrrrr}
\toprule
 & fGFPCA & GLMMadaptive & GFOSR (L=1) & GFOSR (L=5)\\
\midrule
Simulation 1 & 2.584 & 2.304 & 0.025 & 0.144\\
Simulation 2 & 2.415 & 5.479 & 0.010 & 0.054\\
\bottomrule
\end{longtable}

\section{NHANES data application}\label{nhanes-data-application}

@@

\subsection{AUC}\label{auc}

@@

\begin{landscape}
\begin{longtable}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{12}{c}{Maximum observation time} \\
\cmidrule(l{3pt}r{3pt}){2-13}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{fGFPCA} & \multicolumn{3}{c}{GFOSR (L=5)} & \multicolumn{3}{c}{GFOSR (L=1)} & \multicolumn{3}{c}{GLMMadaptive} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
Window & 6am & 12pm & 6pm & 6am & 12pm & 6pm & 6am & 12pm & 6pm & 6am & 12pm & 6pm\\
\midrule
6am-12pm & 0.701 &  &  & 0.689 &  &  & 0.684 &  &  & 0.581 &  & \\
12pm-6pm & 0.530 & 0.708 &  & 0.519 & 0.699 &  & 0.520 & 0.654 &  & 0.532 & 0.701 & \\
6pm-12am & 0.708 & 0.679 & 0.774 & 0.677 & 0.678 & 0.723 & 0.677 & 0.676 & 0.708 & 0.514 & 0.565 & 0.626\\
\bottomrule
\end{longtable}
\end{landscape}

\subsection{Figure}\label{figure-1}

@@

\includegraphics{manuscript_files/figure-latex/fig_appl_paper-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# selct four subjects}
\NormalTok{plot\_id }\OtherTok{\textless{}{-}} \FunctionTok{sort}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{64198}\NormalTok{, }\DecValTok{80517}\NormalTok{))}

\includegraphics{manuscript_files/figure-latex/fig_appl_pre-1.pdf}

@@
